---
title: "White Wine Quality Exploration"
author: Lin LI
date: August 22, 2017
output: html_document
---


```{r echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
echo=FALSE, warning=FALSE, message=FALSE)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
library(ggplot2)
library(ggthemes)
library(dplyr)
library(tidyr)
library(gridExtra)
library(ggthemes)
library(GGally)
library(corrplot)
theme_set(theme_fivethirtyeight(base_size = 10))
```

# About the Data 

This report explores a dataset which contains 4,898 white wines with 11 \
variables on quantifying the chemical properties of each wine. At least 3 wine \
experts rated the quality of each wine, providing a rating betweern 0 (very \
bad) and 10 (very excellent).

```{r echo=FALSE, Load_the_Data}
#setwd("C:/Users/l-li/Desktop/EDA")
wine <- read.csv("wineQualityWhites.csv")
str(wine)
wine$X <- NULL
names(wine)
summary(wine)
table(wine$quality)
wine$quality <- ordered(wine$quality, levels = c(1:10))
```

We dropped the column `X` which appears to be the row number. `quality` is an \
ordered categorical variable with score between 0 and 10. It's interesting \
to see that our wine experts don't rate the wines as extreme as of score 0 \
(very bad), 1, 2, or 10 (very excellent). The actual range is from 3 to 9 with \
median at 6. The rest of variables are continuous variables which makes sense \
since they represents the amount of the corresponding substance in the wine, \
based on physicochemical tests. 


# Univariate Plots Section

```{r echo=FALSE, quality_histogram}
median_quality <- median(as.numeric(wine$quality), na.rm = T)
mean_quality <- mean(as.numeric(wine$quality), na.rm = T)

ggplot(data = wine, aes(x = as.numeric(quality))) +
  geom_histogram(stat='count', fill = I('#3F51B5')) + 
  ggtitle('Histogram of quality counts') +
  geom_vline(aes(xintercept = as.numeric(median_quality)),
              color = I('#FFC107'),
              linetype='dashed', size=1) +
  geom_vline(aes(xintercept = as.numeric(mean_quality)),
             color = I('#FFC107'),
             size=1) +
  scale_x_continuous(breaks=c(seq(3,9,1))) +
  theme_fivethirtyeight() +
  theme(plot.title = element_text(size = 20, face = 'plain', hjust = 0.5))

```

From this histogram of quality counts, we can see it's a normal distribution \
with mean (solid line) and median (dashed line) with almost the same value. \
Most of the white wine has a quality of 6, and second place is 5. 

```{r echo=FALSE, Pareto_principle}
table(wine$quality %in% c(7, 8, 9))
wine$type <- ifelse(wine$quality %in% c(7,8,9), "premium", "midiocre")
table(wine$type)
```

I remember my wine teacher always talks about Pareto principle (80/20 rule) \
in the wine industry (Yes, I had a wine teacher). Wine of quality 7, 8, 9 \
makes up 27.6% of the total number of white wines rated. Therefore, we will \
consider quality of 7, 8, 9 as premium. 


```{r echo=FALSE, SO2_histogram}
p1 <- ggplot(data = wine, aes(x = total.sulfur.dioxide)) +
  geom_histogram(color='white', fill = I('#7986CB')) +
  theme_fivethirtyeight() +
  ggtitle(bquote("Histogram of total SO"[2])) +
  geom_vline(aes(xintercept=210), size=1, color=I('#FFC107')) +
  geom_text(label="210 mg/L", y=500, x = 270, color=I('#FFC107')) +
  theme(plot.title = element_text(size = 15, hjust = 0.5))
p2 <- ggplot(data = wine, aes(x = free.sulfur.dioxide)) +
  geom_histogram(color='white', fill = I('#3F51B5')) +
  theme_fivethirtyeight() +
  ggtitle(bquote("Histogram of free SO"[2])) +
  theme(plot.title = element_text(size = 15, hjust = 0.5))
p3 <- ggplot(data = wine, aes(x = sulphates)) +
  geom_histogram(color='white', fill = I('#283593')) +
  theme_fivethirtyeight() +
  ggtitle(bquote("Histogram of total sulphates")) +
  theme(plot.title = element_text(size = 15, face = "plain", hjust = 0.5))

grid.arrange(p1,p2,p3, ncol=2)

table(wine$total.sulfur.dioxide>=210)
```

> All wines contains sulphur dioxide in various forms, collectively known as \
sulphites. Even in completely unsulphured wine it is present at concentration \
of up to 10 mg/L. Commercially-made wines contain from ten to twenty times \
that amount. (Source: \
[morethanorganic](http://www.morethanorganic.com/sulphur-in-the-bottle))

Reasons why SO~2~ is not desirable in wine:

* taste: unpleasant smell
* health: potentially fatal allergic reactions
* principle: naturalness in wine

According to EU law, the maximum permitted level of SO~2~ in white/rose wine \
is 210 mg/l. As you can see in the first histogram, there are 285 wines \
exceeded this limit. And we can observe that all three of them have a \
right-skewed distribution. This might be due to the restriction of the \
sulphate and most of the vineyards would obey the rules and avoid exceeding \
the limit.


```{r acidity}
p1 <- ggplot(data = wine, aes(x = fixed.acidity)) +
  geom_histogram(color='white', fill = I('#FF9800')) +
  theme_fivethirtyeight() +
  ggtitle(bquote("Histogram of fixed acidity (tartaric acid) g/dm"^3)) +
  theme(plot.title = element_text(size = 15, face = "plain", hjust = 0.5))

p2 <- ggplot(data = wine, aes(x = volatile.acidity)) +
  geom_histogram(color='white', fill = I('#FF9800')) +
  theme_fivethirtyeight() +
  ggtitle(bquote("Histogram of volatile acidity (acetic acid) g/dm"^3)) +
  theme(plot.title = element_text(size = 15, face = "plain", hjust = 0.5))

p3 <- ggplot(data = wine, aes(x = citric.acid)) +
  geom_histogram(color='white', fill = I('#FF9800')) +
  theme_fivethirtyeight() +
  ggtitle(bquote("Histogram of citric acid g/dm"^3)) +
  theme(plot.title = element_text(size = 15, face = "plain", hjust = 0.5))

p4 <- ggplot(data = wine, aes(x = pH)) +
  geom_histogram(color='white', fill = I('#FF9800')) +
  theme_fivethirtyeight() +
  ggtitle(bquote("Histogram of PH")) +
  geom_vline(aes(xintercept=median(pH)), size=1, color=I('#A1887F')) +
  theme(plot.title = element_text(size = 15, face = "plain", hjust = 0.5))

grid.arrange(p1, p2, p3, p4, ncol=2)

mean(wine$pH)
median(wine$pH)
```

In this set of histograms, we explore the acidity in wines. We have the first \
three variables which are the amount of corresponding acid found in the wines. \
The fourth variable `pH` indicates the acidity level where 7 is neutral and \
smaller the value is, more acidic the liquid is. We observe a right skewed \
distribution of the first three and a normal distribution of PH with median \
and mean at 3.18 (acidic). It makes sense to have the PH histogram not right \
skewed as the above 3 ones since the outliers in the acidity histogram would \
have a lower PH value (tail on the left of PH histogram). 

```{r suger_and_salt}

p1 <- ggplot(data = wine, aes(x = residual.sugar)) +
  geom_histogram(color='white', fill = I('#F8BBD0')) +
  theme_fivethirtyeight() +
  ggtitle(bquote("Histogram of residual sugar g/dm"^3)) +
  theme(plot.title = element_text(size = 15, face = "plain", hjust = 0.5))

p2 <- ggplot(data = wine, aes(x = chlorides)) +
  geom_histogram(color='white', fill = I('#64B5F6')) +
  theme_fivethirtyeight() +
  ggtitle(bquote("Histogram of salt (NaCl) g/dm"^3))  +
  theme(plot.title = element_text(size = 15, face = "plain", hjust = 0.5))
p3 <- ggplot(data = wine, aes(x = density)) +
  geom_histogram(color='white', fill = I('#8BC34A')) +
  theme_fivethirtyeight() +
  ggtitle(bquote("Histogram of density g/cm"^3))  +
  theme(plot.title = element_text(size = 15, face = "plain", hjust = 0.5))

p4 <- ggplot(data = wine, aes(x = alcohol)) +
  geom_histogram(color='white', fill = I('#FFC107')) +
  theme_fivethirtyeight() +
  ggtitle(bquote("Histogram of alcohol %"))  +
  theme(plot.title = element_text(size = 15, face = "plain", hjust = 0.5))

grid.arrange(p1, p2, p3, p4, ncol=2)
```

Some people believe that sweeter a wine is, the more alcohol it should \
contain. We cannot tell this just by looking at the histogram here yet. We \
will more into it in the bivariate plot section. Here we can see both residual \
sugar and salt have very right skewed distribution. And the amount of salt is \
really tiny for all white wines with maximum of 0.346 g/L. Histogram of \
alcohol is a bit right skewed with peaks at around 9 - 9.5 %, it also is quite \
uniform distributed other than the peak points. Most wines have alcohol level \
of 8.5 - 12 %. 

```{r log_sugar}

p1 <- ggplot(data = wine, aes(x = residual.sugar)) +
  geom_freqpoly(aes(color=type))+
  theme_fivethirtyeight() +
  ggtitle(bquote("Histogram of residual sugar g/dm"^3)) +
  theme(axis.title = element_text(), 
        plot.title = element_text(size = 15, face = "plain", hjust = 0.5)) 

p1 + scale_x_log10(breaks = seq(1, 10, 1)) +
  ggtitle(expression("Logscaled histogram of residual sugar"~g/dm^3))

```

We take `residual sugar` only and add the feature of `type` to observe the \
distributions for wines of both types. Log transformation is used here to \
make the right skewed distribution look more standard. 

We can see the shape are overall similar. With most wines have between 1 to 20 \
g/dm^3^ of residual sugar. Mediocre wine has a distinguishable bimodal normal \
distribution with peaks at 1.7 and 8. Distribution of premium wines has three \
peaks at 1.7, 5 and 13.5, but differences between local minimas and maximias \
are not as extreme as those of mediocre wines. 



# Univariate Analysis

### What is the structure of your dataset?

The white wine quality dataset consists of 4898 observations and 12 variables. \
Each observation is a white variant of the Portuguese "Vinho Verde" wine. \
Among the 12 variables, there are 11 input variables (numeric) which represent \
the amount of corresponding substance existing in the wine based on \
physicochemical tests. The output variable `quality` is based on sensory data \
(median of at least 3 evaluations made by wine experts), and it is an ordered \
categorical data with range between 0 (very bad) and 10 (very excellent).

### What is/are the main feature(s) of interest in your dataset?

The main feature of interest is `quality`. I am curious in knowing how does \
the amount of other factors affect the rating from the wine experts. 

### What other features in the dataset do you think will help support your \
investigation into your feature(s) of interest?

By reading the [description of the dataset here ](https://s3.amazonaws.com/udacity-hosted-downloads/ud651/wineQualityInfo.txt),\
I think `volatile acidity`, `citric acid`, `free sulfur dioxide`, \
`total sulfur dioxide`, `density` may support my investigation. Because they \
seems to affect the smell, taste and color. `density` may contribute to the \
effect of "wine curtains" which is also a essential part of wine tasting. 

### Did you create any new variables from existing variables in the dataset?

Yes, I created a new categorical variable `type` to indicate whether a wine \
is `premium` or `mediocre` where `premium` wines are the ones rated above 7 \
quality and `mediocre` the rest.

### Of the features you investigated, were there any unusual distributions? \
Did you perform any operations on the data to tidy, adjust, or change the form \
of the data? If so, why did you do this?

I dropped the column `X` which appears to be the row number. I also changed \
`quality` to a ordered categorical variable with score between 0 and 10.

Many variables have a right skewed distribution with outliers on the far end \
of the tail. However, `quality` is quite normal distribution with no extreme \
value like 0, 1, 2, or 10. I haven't removed the "outliers" from the dataset \
because at this point I am not sure if their extremeness contribute to the \
feature of interest.


# Bivariate Plots Section

```{r echo=FALSE, scatterplot_matrix}
set.seed(42)
ggpairs(wine, axisLabels = 'none')

```

This scatterplot matrix with all variables gives broad overview of what \
variables might be interesting.

```{r}
corrplot(cor(wine %>% na.omit() %>% select_if(is.numeric), method = "pearson"),
         method='ellipse',
         order="AOE", tl.cex=1, tl.col="#604c4c")
```

This correlation plot shows more clearly about the correlation between \
variables.


```{r boxplots}

numFeatures <- names(wine)[1:11]
listFeatures <- list()

for(i in 1:length(numFeatures)){
  y = numFeatures[i]
  title <- paste(y,"vs. quality")
  
  listFeatures[[i]] <- wine %>% na.omit() %>% 
    ggplot(aes_string(x = wine$quality, y = y, color=y)) +
    geom_boxplot(colour='#0b421a',size=.5,alpha=.5) +
    geom_jitter(shape=16,width=.2,size=1, alpha=0.05) +
    ggtitle(title) + coord_flip() +
    scale_color_gradientn(
      colours=colorRampPalette(c("#eac784","#362415"))(20)) +
    theme(legend.position='none',
          axis.title = element_text(),
          axis.title.x = element_text(size = 8),
          plot.title = element_text(size = 10, face = 'plain', hjust = 0.5)) +
    labs(x = "",
         y = y)
}

do.call(grid.arrange, c(listFeatures, ncol=3))

```

An interesting observation is that the outliers they happen more at the \
middle range qualities (5, 6, 7) than the extreme values. Very small amounts \
of outliers can be observed for 9-quality or 3-quality wines.

If you look at the boxplot at quality 9 for each factor, notice that the "box" \
is generally smaller than other qualities (especially `density`, \
`sulfur.dioxide`). This suggests that there is a specific set of \
charateristics in order to be rated as an "very excellent" quality Portuguese \
"Vinho Verde" white wine. At this point, I'm impressed by the wine experts who \
rated these wines. Just by blind tasting, they can detect the excellent wine \
with the exact right amount of each substances. 


```{r boxplot_alcohol}
wine %>% na.omit() %>% 
  ggplot(aes(x = quality, y = alcohol, color = alcohol)) +
   geom_boxplot(colour='#0b421a',size=1,alpha=.5) +
    geom_jitter(shape=16,width=.2,size=3, alpha=0.05) +
    ggtitle("alcohol per quality level") + coord_flip() +
    scale_color_gradientn(
      colours=colorRampPalette(c("#eac784","#362415"))(20)) +
    theme(legend.position='none',
          axis.title = element_text(),
          axis.title.x = element_text(size = 10),
          plot.title = element_text(hjust = 0.5)) +
    labs(x = "",
         y = "alcohol in %") 

```

I really like this boxplot of `alcohol`. To reach a `quality` of `9`, alcohol \
level has to be precisely around `12.5%`. However, for other wines at same \
quality, the alcohol level can have 6% in difference. Overall, there is a \
trend starting from level 5 up of more alcohol, better the wine. 


```{r sugar_density}

wine %>% na.omit() %>% 
  ggplot(aes(x = residual.sugar, y = density)) +
  geom_point(alpha=0.2) +
  theme(axis.title = element_text()) +
  ggtitle("Sugar vs. Density") +
  geom_smooth(method = "lm")

```

Looking at this scatterplot between `residual.sugar` and `density`, we can \
spot a positive correlation between the two variables. An outlier can also be \
spotted, it seems to be a good data with extreme value since it still respects \
the `density`, `residual.sugar` correlation, but it just has an extreme high \
`residual.sugar` level. It must be a really sweet wine. We will eliminate this \
outlier from out spot and suset our data with `residual.sugar` less than 30 \
g/dm^3^. 


```{r sugar_density_no_outlier}

wine %>% na.omit() %>% 
  subset(residual.sugar < 30) %>% 
  ggplot(aes(x = residual.sugar, y = density)) +
  geom_point(alpha=0.2) +
  theme(axis.title = element_text()) +
  ggtitle("Sugar vs. Density") +
  geom_smooth(se=F, method = "lm") +
  scale_x_continuous(breaks=seq(0, 30, 5))

```


Something interesting is happening here. Overall, the linear smooth line fits \
well on the scatterplot. However, lower the `residual.sugar` level, wider the \
range of `density` at the same `residual.sugar` level. My guess is when \
`residual.sugar` level is low, `density` can be correlated with a third \
variables.

# Bivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. How did the feature(s) of interest vary with other features in \
the dataset?

From the set of boxplots, we can observe that `alcohol` seems to be \
appreciated. With higher alcohol level, the median rating of quality is \
generally higher. 

`pH`, `fixed.acid` and `citric acid` shows slight positive correlation as well. 

On the other side, `sulfur.oxide`, `sugar`, and `density` are not appreciated, \
negatively correlated to quality.


### Did you observe any interesting relationships between the other features \
(not the main feature(s) of interest)?

We can observe that there is strong (0.853) correlation between `density` and \
`residual.sugar` which is what I suspected before.

It's only nutural to see that `free.sulfur.dioxide` and `total.sulfur dioxide` \
has a correlation of 0.61.

Also as suspected before, `sugar` and `density` has a strong correlation \
of 0.839. All other factors somewhat contribute to `density` a bit as we can \
see the correlation ranges from 0.15 to 0.839 for `density` with other factors \
except for the factor `volatile acidity` (corr: 0.0271).

Surprisingly, `alcohol` and `residual.sugar` have a negative correlation \
of -0.427. `alcohol` and `density` also have a strong negative correlation of \
-0.711, which makes sense since `density` and `residual.sugar` are highly \
positively correlated. 

From the boxplots on the `quality` column, we suspect that `alcohol`, \
`total.sulfur.dioxide`, and `density` have some effects on the ratings of \
wine quality by the wine experts. 


### What was the strongest relationship you found?

The strongest relationship I found is between `residual.sugar` and `density`. \
They have a correlation of 0.853. `density` and `alcohol` also has a strong \
negative correlation of -0.78.

# Multivariate Plots Section


```{r sugar_density_SO2}

range(wine$total.sulfur.dioxide)

wine$total.sulfur.dioxide.bucket <- 
  with(wine, cut(total.sulfur.dioxide, c(0, 100, 150, 210, 440)))


wine %>% na.omit() %>% subset(residual.sugar < 30) %>% 
  ggplot(aes(x = residual.sugar,
             y = density,
             color= total.sulfur.dioxide.bucket)) +
  geom_point(alpha = 0.05) +
  geom_smooth(method = "lm",
              aes(color = total.sulfur.dioxide.bucket),
              se = F) +
  theme(axis.title = element_text(),
        plot.title = element_text(hjust=0.5, size=20)) +
  ggtitle(expression("sugar vs density by total"~SO[2]))
  
```

Following previous analysis between `residual.sugar` and `density`, \
`total.sulfur.dioxide` is added as a feature here. I first cut the variable \
into 4 buckets `(0, 100], (100, 150], (150, 210], (210, 440]`. My guess \
earlier was correct. At the same `residual.suagr` level, wines with lower \
`total.sulfur.dioxide` level are less dense. 


```{r sugar_vs_density}

wine %>% na.omit() %>% subset(residual.sugar <= 30) %>% 
  ggplot(aes(x = residual.sugar, y = density, color = quality)) +
  geom_point(alpha=0.2)+ geom_smooth(method = 'lm', se=FALSE)+
  scale_color_brewer(type='qual',
                     palette = 'Set2',
                     guide = guide_legend(title="Quality", 
                                          override.aes = list(alpha=1, size=2)))+
  ggtitle("Sugar vs. Density by Quality") +
  facet_wrap(~quality) +
  theme(axis.title = element_text(),
        plot.title = element_text(hjust = 0.5, size=20)) +
  labs(
    x = expression("residual sugar in "~g/L),
    y = expression("density in "~g/cm^3))
```


```{r sugar_vs_density_by_type}


wine %>% na.omit() %>% subset(residual.sugar < 30) %>% 
  ggplot(aes(x = residual.sugar, y = density)) +
  geom_point(aes(color = type), alpha=0.05) +
  geom_smooth(aes(color = type), method='lm', se=FALSE) +
  scale_color_brewer(type='qual',
                     palette='Set1',
                     guide = guide_legend(title="Quality", 
                                          override.aes = list(alpha=1, size=2)))+
  ggtitle("Sugar vs. Density by Type") +
  theme(axis.title = element_text(),
        plot.title = element_text(hjust = 0.5, size=20)) +
  labs(
    x = expression("residual sugar in "~g/L),
    y = expression("density in "~g/cm^3))

```

To make this set of plots, outliers (`residual.sugar` > 30) are removed from \
the dataset.

We can see that the strong correlation between density and sugar doesn't \
change at no matter what quality. 

Observe the second plot, we can see that at same level of sugar, premium wines \
are less dense than midiocre wines. Mediocre wine also have a bigger range \
of `residual.sugar` level (the outliers we didn't show are also mediocre wines).



```{r SO2_density_by_type}

wine %>% na.omit() %>% subset(residual.sugar <= 30) %>% 
  ggplot(aes(x = total.sulfur.dioxide, y = density, color = type)) +
  geom_point(alpha=0.1) + geom_smooth(aes(color = type), method='lm', se=FALSE) +
  scale_color_brewer(type='qual',
                     palette = 'Set2',
                     guide = guide_legend(title="Quality", 
                                          override.aes = list(alpha=1, size=2)))+
  ggtitle("Total sulfur dioxide vs Density by Type") +
  theme(axis.title = element_text(),
        plot.title = element_text(hjust = 0.5, size=20)) +
  labs(
    x = expression("total sulfur dioxide in"~mg/dm^3),
    y = expression("density in "~g/cm^3))

```


`total.sulfur.dioxide` and `density` are not as correlated `sugar` with \
`density` but we can observe the same trend that the line of fit for `premium` \
is lower than `midiocre`. 


# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. Were there features that strengthened each other in terms of \
looking at your feature(s) of interest?


`sugar` and `density` seems to strengthen each other in terms of looking at \
`quality`. At the same `sugar` level, `premium` wines tend to have less \
`density` than `mediocre` wines. Extremely high `sugar` level has lower chance \
of being rated as excellent wines.


### Were there any interesting or surprising interactions between features?

Wines at quality levele 5, 6, 7 always have extreme level in features like \
`residual.sugar` and `sulfur.dioxide`. This is surprising as they are not \
rated as bad wines (level 2,3) but OK wines. 

------

# Final Plots and Summary

### Plot One
```{r echo=FALSE, Plot_One}

ggplot(data = wine, aes(x = as.numeric(quality))) +
  geom_histogram(stat='count', fill = I('#3F51B5')) + 
  ggtitle('Histogram of quality counts') +
  geom_vline(aes(xintercept = as.numeric(median_quality)),
              color = I('#FFC107'),
              linetype='dashed', size=1) +
  geom_vline(aes(xintercept = as.numeric(mean_quality)),
             color = I('#FFC107'),
             size=1) +
  scale_x_continuous(breaks=c(seq(3,9,1))) +
  theme_fivethirtyeight() +
  theme(axis.title = element_text(),
        plot.title = element_text(size = 20, hjust = 0.5)) +
  labs(
    x = "Quality",
    y = "Count"
  )

```

### Description One

This is a histogram of quality counts of the wines. The dashed lines is the \
median and solid line is mean. We can see that it's a normal distribution with \
mean and median at 6. 


### Plot Two
```{r echo=FALSE, Plot_Two}

wine %>% na.omit() %>% subset(residual.sugar < 30) %>% 
  ggplot(aes(x = residual.sugar,
             y = density,
             color= total.sulfur.dioxide.bucket)) +
  geom_point(alpha = 0.05) +
  geom_smooth(method = "lm",
              aes(color = total.sulfur.dioxide.bucket),
              se = F) +
  theme(axis.title = element_text(),
        plot.title = element_text(size = 20, hjust = 0.5)) +
  ggtitle(expression("Residual Sugar vs Density by Total"~SO[2])) +
  labs(
    x = expression("Residual Sugar in"~g/dm^3),
    y = expression("Density in"~g/cm^3)
  ) +
  scale_color_brewer(palette='YlOrBr',
                     guide = guide_legend(title = expression("Total"~SO^2),
                                          override.aes = list(alpha=1, size=2)))

```

### Description Two

This plot has 3 dimensions, `residual.sugar`, `total.sulfur.dioxide.bucket` \
cut from `total.sulfur.dioxide` and `density`. We can observe the positive \
correlation between `residual.suagr` and `density`. At the same \
`residual.suagr` level, wines with lower `total.sulfur.dioxide` level are less \
dense. 


### Plot Three
```{r echo=FALSE, Plot_Three}

wine %>% na.omit() %>% subset(residual.sugar <= 30) %>% 
  ggplot(aes(x = residual.sugar, y = density)) +
  geom_point(aes(color = type), alpha=0.05) +
  geom_smooth(aes(color = type), method='lm', se=FALSE) +
  scale_color_brewer(type='qual',
                     palette='Set1',
                     guide = guide_legend(title="Quality", 
                                          override.aes = list(alpha=1, size=2)))+
  ggtitle("Sugar vs. Density by Type") +
  theme(axis.title = element_text(),
        plot.title = element_text(hjust = 0.5, size=20)) +
  labs(
    x = expression("Residual Sugar in "~g/dm^3),
    y = expression("Density in "~g/cm^3))

```

### Description Three

From this plot, we can see that at same level of sugar, premium wines are less \
dense than midiocre wines. Mediocre wine also have a bigger range of \
`residual.sugar` level (the outliers we didn't show here are also mediocre \
wines). 

------

# Reflection

At the beginning it was hard to understand what does each numeric variables \
mean and how could they affect the quality of wine. After doing some research \
and read more carefully on the documentation of the dataset, it became more \
clear how I could explore this dataset. Another struggle is that there is \
really subtle differences in the amount of variables, you can see from the \
scatterplots that all the points are kind of all cluster together, it's hard \
to visualize when you just put quality as color in the same scatterplot. Maybe \
some tranformation of data could be used in the future, to make it possible to \
visually separate the clusters. 

